Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-22 content/contribution/CoDeR.tex
started work on the algebra, starting with a summary then moving to detailed descriptions of each operatior

	% Minimal Algebra

>>>>

	% Minimal Algebra
	\begin{nestedsection}{Minimal Algebra}{model: algebra}
		The minimal algebra of CoDeR is based on that of Positive Datalog, that being ${\{\bot, \text{:-}, \wedge\}}$.
		Of these, $\text{:-}$ and $\wedge$ may be expressed as stream-to-stream operators, the former being trivially incremental and the latter being the window-join \citep{ReteDBMS}, in order to support forward-chaining processing of fixed rules;
		$\bot$ is not an operator, but a special class of value represented in CoDeR by the ${rif\text{:}error()}$ class from RIF \citep{w3crif}).
		Further, in order to support both fixed-plan pattern-matching algorithms such as the Rete algorithm \citep{forgy79} and adaptive algorithms such as the Eddies algorithm \citep{eddies} and its derivatives \citep{CACQ,TCQ}, CoDeR replaces the window-join operator with the State Module of Eddies, algebraically represented by ${{}_b\Join_p}$.
		In addition to $\text{:-}$ and $\wedge$, CoDeR utilises a pair of stream-filter operators, $\sigma_{triple}$ and $\sigma_{external}$, for identifying \emph{basic patterns} as defined in SPARQL \citep{w3csparql} and the datatype functions of RIF-Core \citep{w3crifcore}.
		Finally, as basic patterns match individual triples, the CoDeR algebra includes a graph-to-triples operator ${{}_g\pi_t}$ to translate streams $S$ from the streams of graphs recommended by the RSP community to the streams of triples on which $\sigma_{triple}$ operate.
		In summary, the minimal algebra of CoDeR consists of the set of operators ${\{\text{:-}, {}_b\Join_p, \sigma_{triple}, \sigma_{external}, {}_g\pi_t\}}$.

		\begin{description}
			\item[$\sigma_{triple}$] \hfill \\
				The \emph{basic pattern match} of SPARQL is one-pass, and so is trivially interpreted as the stream-to-stream operator $\sigma_{(s,p,o)}$.
				It takes a stream of triple instances as input and produces a stream of triple instances that contains a subset of those instances in the input stream, maintaining the ordering of those instances.
				The contents of the produced stream are characterised as those triple instances from the input stream whose triples match the basic pattern ${(s,p,o)}$.
			\item[$\sigma_{external}$] \hfill \\
				This operator encompasses all of the one-pass built-in datatype functions of RIF-Core, and is also trivially interpreted as a stream-to-stream operator $\sigma_{f(a_1,\dots,a_n)}$, where each ${a_1,\dots,a_n}$ is either a variable or a constant value.
				It filters instances from its single input stream to a stream of instances that contains a subset of those instances in the input stream, maintaining the ordering of those instances.
				This filtering is based not on the semantic structure of the data but directly on the values of variables, which are consistent throughout any given graph pattern, thus the $\sigma_{external}$ operator expresses an \emph{advanced} component of an \emph{advanced graph pattern};
				as such, the contents of the produced stream are characterised as those graph instances from the input stream whose graphs match a specific advanced graph pattern.
		\end{description}
	\end{nestedsection}
